%====================
% VP Engineering and AI at jejakin.com
%====================
\subsection{{VP Engineering and AI \hfill May 2024 --- Present}}
\subtext{jejakin.com \hfill Engineering, AI and Data Lead}
\begin{zitemize}
    \item Leading and coaching Data and AI Engineering team to build intelligent carbon project management systems.
    \item Helping product team identify AI potential to optimize business flow and features, especially the Atlas product for automated land cover analysis from satellite images (Google Earth) and CO2e economics optimization recommendations.
    \item Built new version of pre-feasibility stage with automation features for activity analysis using deep learning for land cover analysis.
    \item Setup self-hosted LLM model for report generation automation and client assistance. Fine-tuned LLM with VERRA standard and Sistem Registri Nasional (SRN).
    \item Built better AI platform with pipeline and packages/libraries to improve delivery process.
    \item Set up pipeline for Data team and standard operations for efficient data engineering.
    \item Mentoring data science team to provide insights for management on current business conditions and KPIs.
    \item Analyzing fraud cases in partner onboarding and monitoring to ensure reforestation programs meet schedules and standards.
    \item Helping ISO27701:2019 and ISO27001:2022 compliance for Data Masking and Data Loss Prevention.
    \item Secured Google Cloud startup program credit (1 year, ~IDR 1.8 Bio).
\end{zitemize}

%====================
% Principal R&D and Head of Data at PT. Akart Inti Data
%====================
\subsection{{Principal R\&D and Head of Data \hfill Oct 2022 --- Apr 2024}}
\subtext{PT. Akart Inti Data \hfill R\&D and Data}
\begin{zitemize}
    \item Led Data team on several data projects and developed advanced data analytics platforms (Python, Scala, Apache Spark, Play).
    \item Improved nusadata.ai scalability and initiated AISight as new advanced data platform product.
    \item Architected AISight as advanced data platform to handle big data pipelines integrated with nusadata.ai as one-stop platform for data exchange and processing.
    \item Automated data analytics process with robust AISight platform.
    \item Designed and built geographical business performance system to automate area identification for retail store expansion.
    \item Designed and built data enrichment and lead generation service as AISight features.
    \item Built Big Data environment handling 2TB (10 billion people mobility data) and 49GB (130 million people data). Helped PT. Pertamina Retail build dashboard for 3TB transaction data.
    \item Designed and built general fraud detection system using rule-based and machine learning approaches.
    \item Designed and built billboard performance scoring system using digital mobility data.
    \item Served and analyzed consent management system using 3rd party partner (security.ai).
    \item Designed and built Encryption as a Service system (Secret Base) for Data in Use Encryption, advocating UU PDP compliance.
    \item Worked as solution architect providing solutions for Nusadata and AISight clients.
    \item Supervised, mentored, and guided multiple tech teams, especially data team.
    \item Conducted R\&D to improve base systems (nusadata, AISight) and Secure Multi-Party Computation (SMPC).
    \item Integrated advanced analytics platform to SMPC 3rd party service as short-term solution for secure analytics.
    \item Helped compliance with ISO27001:2013 and ISO27001:2022.
    \item Temporarily served as PIC for Tech Team, leading data and software engineering teams.
    \item Redesigned infra architecture for nusadata.ai and AISight, reducing costs by 50\%.
    \item Helped HR create Man Power Planning, improve recruitment, set Learning \& Development programs, and review KPI/OKR.
    \item Re-architected AISight to be Cloud Agnostic. Migrated PT. Pertamina Ritel platform from GCP to Huawei.
    \item Architected data platform integrating transaction data from switching company for 50+ apps for data monetization while maintaining compliance.
\end{zitemize}

%====================
% Technical Lead at Finantier.co
%====================
\subsection{{Technical Lead \hfill March 2022 --- Oct 2022}}
\subtext{Finantier.co \hfill Platform for open finance}
\begin{zitemize}
    \item Tech Lead for Platform and Product: Re-architected platform to improve performance, efficiency, and asynchronous processing.
    \item Centralized encryption service using Vault (transit) for data in use encryption.
    \item Developed Golang library to simplify encryption/decryption process, improving developer experience and security.
    \item Implemented "data in use" encryption with multiple policies based on data classification.
    \item Designed Notification service to support messaging features and asynchronous processes.
    \item Helped Engineering team (especially backend) review and construct solutions for business needs.
    \item Researched Central Authentication Service (CAS) for internal system.
    \item Developed credit scoring and eKYC apps, integrating with multiple data sources.
    \item Developed simple subscription feature for credit-scoring app.
    \item Coached development team for platform and product app.
\end{zitemize}

%====================
% Consultant at rumaysho.com
%====================
\subsection{{Software Architect Consultant \hfill June 2021 --- Present}}
\subtext{rumaysho.com (rumayshoacademy.com) \hfill Non-commercial}
\begin{zitemize}
    \item Part-time consultant creating apps for Islamic education activities and building IT Department.
    \item Developed online course app (rumayshoacademy.com) starting with Moodle (Version 1).
    \item Rewrote online course from scratch with Vue.js frontend and Kotlin Spring Boot backend (MongoDB, Elastic) to improve performance, clean code, scalability, and security (Version 2).
    \item Improved concurrency capability supporting simultaneous exams (3000 concurrent users) through architecture redesign.
    \item Designed microservices architecture for internal and end-user systems.
    \item Designed and implemented new infrastructure on local VPS with CI/CD.
    \item Recruited and managed engineering teams, implementing agile flow and culture (built IT Team from scratch).
    \item Developed payment system for rumaysho group on top of IPG (Midtrans) for education and merchandising.
\end{zitemize}

%====================
% Principal R&D Engineer at Blibli.com
%====================
\subsection{{Principal R\&D Engineer \hfill Oct 2019 --- Feb 2022}}
\subtext{Blibli.com \hfill AI Squad \& DevEx Squad}
\begin{zitemize}
    \item Led AI squad in R\&D Team (Informally).
    \item Set up Jenkins CI pipeline for each technology used by blibli.com (Java, Golang, Python).
    \item Setup tools and repositories for docker base images for each technology.
    \item Developed new graph rule engine (REST Backend) using microkernel architecture for customer grouping (promo abuser analysis).
    \item Migrated CI from Bamboo to Jenkins and helped other teams onboard.
    \item Researched relevant approaches for string clustering (email), finding faster and more effective approach for abuser cases.
    \item Mentored interns for research and developing customer clustering app on new ML engine. Mentored final project for automatic add-to-cart using computer vision for blibli offline store (bliblimart).
    \item Developed new general rule engine (REST Backend) using microkernel architecture for return anomaly cases.
    \item Migrated engine from Scala to Python and implemented TensorFlow.
    \item Researched and implemented Hidden Markov Model for dynamic collaborative filtering using Scala, Akka, and MongoDB, then rewrote to Python stack.
    \item Data engineering using Kafka for stream processing.
    \item Speaker at Deep Learning Summit 2017 in Singapore (re:work): "Against Fraudulent Transaction with Deep Neural Network".
\end{zitemize}

%====================
% Senior Software Development Engineer at Blibli.com
%====================
\subsection{{Senior Software Development Engineer \hfill Dec 2015 --- March 2017}}
\subtext{Blibli.com \hfill Fraud System}
\begin{zitemize}
    \item Developed fraud detection system for online transactions using rule-based approach (Java, Spring).
    \item Data migration from RDBMS to MongoDB (Scala with Akka).
    \item Migrated search feature from MongoDB to Elasticsearch.
    \item Rule engine architecture revamp and code refactoring for Sonar compliance and unit test coverage.
    \item Used ID-Tree Algorithm for Rule Generator.
\end{zitemize}

%====================
% Data Scientist at PT. Starlabs Global Teknologi
%====================
\subsection{{Data Scientist (Co-Founder) \hfill April 2015 --- November 2015}}
\subtext{PT. Starlabs Global Teknologi \hfill Co-Founder}
\begin{zitemize}
    \item Developed Deep Learning algorithm implementation from scratch (Scala).
    \item R\&D for GDP (Gross Domestic Product) Prediction for Indonesia.
    \item Experimented with deep networks using stack autoencoder and stack-restricted Boltzmann machine (Scala). Used Hadoop and Spark.
    \item Developed stack of methods for social media analysis and Averi Project (Twitter prostitution account identifier) using machine learning.
    \item Averi app won Indonesia ICT Award 2015 for R\&D category.
\end{zitemize}

%====================
% Software Engineer at Veritrans Indonesia (Now: Midtrans)
%====================
\subsection{{Software Engineer \hfill Feb 2014 --- January 2015}}
\subtext{Veritrans Indonesia (Now: Midtrans) \hfill }
\begin{zitemize}
    \item Developed Fraud Detection System using Machine Learning (research and implementation).
    \item Implemented backpropagation and random forest algorithms for fraud detection (Scala).
    \item Developed API for fraud detection system using Play framework.
    \item Developed machine learning from scratch.
\end{zitemize}

%====================
% Lecturer at STMIK Tazkia
%====================
\subsection{{Lecturer \hfill April 2022 --- Present}}
\subtext{STMIK Tazkia \hfill Bogor}
\begin{zitemize}
    \item Lecturer for Artificial Intelligence, Data Engineering, and Machine Learning.
\end{zitemize}

%====================
% Lecturer at Universitas Komputer Indonesia (UNIKOM)
%====================
\subsection{{Lecturer \hfill Feb 2012 --- Feb 2014}}
\subtext{Universitas Komputer Indonesia (UNIKOM) \hfill Bandung}
\begin{zitemize}
    \item Lecture for Introduction of Algorithm, Analysis and Design of Algorithm, Computer Graphics, Image Processing.
\end{zitemize}
